---
title: "Encapsulation"
subtitle: "Importing shp format data"
drake_cache: ".chartTaiwanMap"
output: html_document
---

```{r setup, include=FALSE, drake=F}
knitr::opts_chunk$set(echo = TRUE, eval=F)
```

```{r echo=F, eval=T}
library(klippy)
klippy::klippy()
```

------------------------------------------------------------------------

## makecondition

```{r makecondition}
library(sf)

library(dplyr)
library(stringr)
library(ggplot2)
library(econDV)
```

## Encapsulation {.tabset}

### Blue print

```{r}

# data import
{
  
}
# graph
{
  
}
# simplify
{
  
}
# crop
{
  
}
# zoom
{
  
}
# export
{
  
}
# restore (Throw in for safety)
{
  
}
```

### Pseudocode

Prepare

-   [**ONLY ONE**]{.alert-success} object to save your result.

-   If the result involves with mutiple things, save them within that **ONE** object [**using `$` or `[[resultName]]` operation**]{.alert-success}.

::: {.alert .alert-info}
If result presents an action for users decide to take, it has to be an **function**.
:::

```{r}
# Declare a capsule (# type to be determined)
geoD <-
# data import
geoD$.data <- 
{
  
}
# graph
geoD$graph <- function()
{
  
}
# simplify
geoD$simplify <- function()
{
  
}
# crop
geoD$crop <- function()
{
  
}
# zoom
geoD$zoomIn <- function()
{
  
}
geoD$zoomOut <- function()
{
  
}
# export
geoD$export <- function()  
{
  
}
# restore (Throw in for safety)
geoD$restore <- function()
{
  
}
```

### Pseudocode 2 (Encapsulation)

Save all the data you need and actions (i.e. *function*) you need [**within the same object**]{.alert-success} whose class has to be [**environment**]{.alert-success}.

-   When retrieving any object value, or

-   When saving any object value,

**ALWAYS** refers to its relevant **environment** except intermediate step object values.

```{r}
dataSource <- "/Users/martinl/Dropbox/github-data/109-1-econDV/直轄市、縣市界線(TWD97經緯度)SHP格式/COUNTY_MOI_1090820.shp"

# Declare a capsule (# type to be determined)
geoD <- new.env()
# data import
geoD$.data <- 
{
  sf::st_read(dataSource)  
}
# graph
geoD$graph <- function()
{
  require(dplyr); require(ggplot2)
  geoD$.data %>%
    ggplot()+geom_sf() ->
    geoD$.graph
  
  geoD$.graph
}
# simplify
geoD$simplify <- function()
{
  rmapshaper::ms_simplify(geoD$.data) -> geoD$.data
}
# crop
geoD$crop <- function(...)
{
  argList <- list(...)
  sf::st_crop(
    geoD$.data,
    unlist(argList)
  ) -> geoD$.data
}
# zoom
geoD$zoomIn <- function()
{
  
}
geoD$zoomOut <- function()
{
  
}
# export
geoD$exportData <- function()  
{
  geoD$.data
}
# restore (Throw in for safety)
geoD$restore <- function()
{
  
}
```

### Test 2

```{r}
# initial data size
size0 <- object.size(geoD$.data)
# initial graphing
geoD$graph()
# data too much detail
geoD$simplify()
geoD$graph()
# faster graphing, but want main island
geoD$crop(
 xmin=120, xmax=123,
  ymin=22, ymax=26)
geoD$graph()
geoD$exportData() -> finalGeoData
sizeFinal <- object.size(finalGeoData)
```

### Function prototype

```{r}
GeoData_shp <- function(shpDataSource) {
  assertthat::assert_that(
    stringr::str_detect(
      basename(shpDataSource),
      stringr::regex(
        "shp$",
        ignore_case = T
      )
    ),
    msg = "The data source is not a shp data."
  )
  # Declare a capsule (# type to be determined)
  geoD <- new.env()
  # data import
  geoD$.data <- {
    sf::st_read(shpDataSource)
  }
  # graph
  geoD$graph <- function() {
    require(dplyr)
    require(ggplot2)
    geoD$.data %>%
      ggplot() +
      geom_sf() ->
    geoD$.graph
    geoD$.graph
  }
  # simplify
  geoD$simplify <- function() {
    rmapshaper::ms_simplify(geoD$.data) -> geoD$.data
  }
  # crop
  geoD$crop <- function(...) {
    argList <- list(...)
    sf::st_crop(
      geoD$.data,
      unlist(argList)
    ) -> geoD$.data
  }
  # zoom
  geoD$zoomIn <- function() {

  }
  geoD$zoomOut <- function() {

  }
  # export
  geoD$exportData <- function() {
    geoD$.data
  }
  # restore (Throw in for safety)
  geoD$restore <- function() {

  }
  return(geoD)
}
```

### Function test

```{r}
dataSource <- "/Users/martinl/Dropbox/github-data/109-1-econDV/直轄市、縣市界線(TWD97經緯度)SHP格式/COUNTY_MOI_1090820.shp"

geoD_beta <- GeoData_shp(dataSource)

# data too much detail
geoD_beta$simplify()
geoD_beta$graph()
# faster graphing, but want main island
geoD_beta$crop(
 xmin=120, xmax=123,
  ymin=22, ymax=26)
geoD_beta$graph()
geoD_beta$exportData() -> finalGeoData
```

::: {.alert .alert-info}
GeoData_shp generates an **instance** (情境), *geoD_beta*, whose acting results depends on (1) an **external state** (*dataSource*, like 'exogenous shock' in Economics term) and (2) **dynamic states** (*\$.data*, like 'state variable' in Economics term), and (3) the action and state evolution are all kept within the instance itself (which is called **Encapsulation**(封包設計)).

Instance generator is usually named with *Capital* starting letter in contrast to an instance whose starting letter is in *small case*.
:::

## Exercise

Complete **GeoData_shp** instance initiator.
