---
title: "Function and Execution Environments"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Function environment and Execution Environment

```{r}
greeting <- function(username){
  cat("Hi, ", username)
}
```

-   Function environment: where **greeting** resides.

-   Execution environment: the ephemeral environment when **greeting** function is called.

> **call** is an expression when a function's input arguments' values are supplied so that it is ready to go.

```{r}
greeting # not a call
greeting("John") # is a call
```

> As we can see that function class object can have different statuses, that is different statuses are called different **mode**s. When object has only static status, its class and mode are the same.

### Execution Environment (EE)

#### Falling into the rabbit hole:

```{r}
greeting <- function(username){
  browser() # this is the rabbit hole we create to lead us to the execution environment world.
  cat("Hi, ", username)
}

```

```{r}
greeting("John")

```

### Function environment

#### When things are missing in EE

```{r}
greeting <- function(username){
  cat("Hi, ", username,". I live in ", location, ". ")
}
```

```{r}
greeting("John")
```

```{r}
debug(greeting) # another way to create the rabbit hole.
greeting("John")
```

```{r}
location <- "Sanxia"
greeting("John")

```

> **location** does not have to exist when the function is created---only needed when the function is called (**Lazy Evaluation**).

> **Exist** mean exist in **Functional Environment** (FE) that is where **greeting** resides, or exist in Execution Environment (EE).
>
> -   EE -\> FE

### Scoping rule

#### Genealogy

When something is missing in an environment, how is the program looking for the missing piece? The process of missing piece looking is called **scoping**.

```{r}
greetingPersonFromSameLocation <- function(username){
  browser()
  greeting2 <- function(username){
    browser()
    cat("Hi, ", username,". I live in ", location, ". ")
  }
  greeting2(username)
}
```

-   In R, the scoping rule is based on the genealogy (族譜）of an environment, with an additional restriction: only look at preceding environments, NOT at the succeeding environments.

-   Use `parent.env(an environment)` to look for the parent environment of an environment.

```{r}
location <- "Taipei"
debug(greetingPersonFromSameLocation)
greetingPersonFromSameLocation("John")
```
